% !TEX root = mythesis.tex

%==============================================================================
\chapter{ERA5 Wind Speed Data Analysis}
\label{sec:era5-data}
%==============================================================================
\section{ERA5 Data}
This section introduces the ERA5 dataset (parameters, model levels, simulation and data taking)

introduction similar to Fiona - ref ERA5 documentation

\textit{What are the errors on wind speeds to be expected from ERA5 data?}

include locations inspected in detail: location map

\subsection{Model Level Height Calculation}
Explain principle of height calculation - ref Fiona \& website:  \url{https://confluence.ecmwf.int/display/CKB/ERA5%3A+compute+geopotential+on+model+levels}

\textit{What are the errors on wind speeds and other params - height calc errors?}

impact:\\
sea no change\\ 
land more change - less than paper (see height pdfs?)\\

height/diff pdfs: shapes strongly impacted by local parameters

diff pdfs:\\
in total - consistent with model level and surface elevation calculation
single location diffs - 

\subsection{ERA5 Latitude-Longitude Grid Resolution}
This shows via basic parameters the differences between the previously used rough grid and the now used fine grid (ALPES)\\
mention gaussian grid, interpolation - different meaning of 1x1 and .25x.25 same point

Chosen fine grid

need for parallelisation (larger/more data) - ref to repo? 

\subsection{Yearly Differences}
show average wind speed pdfs for all years at one point for reference (same scales?)\\
Yearly wind speed 100m for full map in appendix? 

roughly quantify variation: max, min and overall mean wind speeds plus variance?

Fiona cyclons / Cologne research reference? 

Year by year differences observed $\rightarrow$ chosen range of 11 years\\

\section{ERA5 Wind Speed Potential Reanalysis}
what is processed? how does the processing work? explain meaning of percentiles: 
\begin{itemize}
\item 5: 95\% of time at least these wind speeds
\item 32:
\item 50: median
\end{itemize}

compare results w/ paper: map for 2011 to 2017 and 2010 to 2020 - changes? \\ 
find update to paper conclusion? 
